### 2021-03-31 Figures/BRMS_Metric_PPCA.Rmd
Plot PPCA with images, still need more edits

Visits_PC1 <- ggplot(ce_1[[1]], aes(x = PC1, y = (estimate__+1))) + geom_point(data = data_analysis2,aes(x = PC1, y = Visits),
       size = 1.5, alpha=0.9) + geom_line(colour="darkblue",size=1.2) + ylim(0,quantile(data_analysis2$Visits, 0.95)) +theme_ms()+
  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1,fill="darkblue") + ylab("Number of visits")+ ggtitle("A")

>>>>

Visits_PC1 <- ggplot(ce_1[[1]], aes(x = PC1, y = (estimate__+1))) + geom_point(data = data_analysis2,aes(x = PC1, y = Visits),
              size = 1.2, alpha=0.9) + geom_line(size=1.2) + ylim(0,quantile(data_analysis2$Visits, 0.95)) +theme_ms()+
              geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1) + ylab("Number of visits") + ggtitle("A")

### 2021-03-31 Figures/PPCA_Plant_Functional_Groups.Rmd
Plot PPCA with images, still need more edits

#############################################################################################################################################################
#COMPATIBILITY
#############################################################################################################################################################
#Load plots
all_spp <- function(PC, x="PC1", y="PC2") {
  # PC being a prcomp object
  data <- data.frame(PC$S)
  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
  dat <- data.frame(x = data[,x], y = data[,y])

@@

  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
  dat$Clusters <- dat_cleaning_5$Clusters
  dat$Clusters <- as.character(dat$Clusters)
  dat$Clusters[dat$Clusters=="1"] <- "A"
  dat$Clusters[dat$Clusters=="2"] <- "B"
  dat$Clusters[dat$Clusters=="3"] <- "C"
  dat$Clusters[dat$Clusters=="4"] <- "D"
  dat$Clusters[dat$Clusters=="5"] <- "E"

 dat$Clusters <- factor(dat$Clusters, levels=c("A", "B", "C", "D", "E"))

  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Clusters),size=2.5)+ scale_color_manual(values =  c("#00AFBB", "#E69F00", "#FC4E07","#000000", "darkgreen"))+ labs(color='Functional groups')

  ########
  #ADD ARROWS 
  ########
  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
  mult <- min(
    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
  )
  datapc <- transform(datapc,
                      v1 = .75 * mult * (get(x)),
                      v2 = .75 * mult * (get(y))
  )
  # add arrows
  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.4, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")

  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")

@@

  #ADD LABELS
  rownames(PC$L) <- c("SELFING", "FLOWER N.", "FLOWER SIZE", "STYLE LENGTH", "OVULE N.", "PLANT HEIGHT" )

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.35,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,5.2,5,7,5.8,6.5)),
                          label = PCAloadings$Variables, color="black",fontface =2,size=5)

@@

>>>>

library(magick)
tree <- image_read("Images/PPCA_Plot/Tree.png")
tree_1 <- as.raster(tree)

style_l <- image_read("Images/PPCA_Plot/Style_Long.png")
style_l_1 <- as.raster(style_l)

style_s <- image_read("Images/PPCA_Plot/Style_Short.png")
style_s_1 <- as.raster(style_s)

ovule_h <- image_read("Images/PPCA_Plot/Ovule_High.png")
ovule_h_1 <- as.raster(ovule_h)

ovule_l <- image_read("Images/PPCA_Plot/Ovule_Low.png")
ovule_l_1 <- as.raster(ovule_l)

selfing_n <- image_read("Images/PPCA_Plot/Selfing_None.png")
selfing_n_1 <- as.raster(selfing_n)

selfing_h <- image_read("Images/PPCA_Plot/Selfing_High.png")
selfing_h_1 <- as.raster(selfing_h)

single_flower <- image_read("Images/PPCA_Plot/Single_Flower.png")
single_flower_1 <- as.raster(single_flower)

many_flowers <- image_read("Images/PPCA_Plot/Many_Flowers.png")
many_flowers_1 <- as.raster(many_flowers)
#many_flowers_1 <- image_rotate(many_flowers, 45)

large_flower <- image_read("Images/PPCA_Plot/Large_Flower.png")
large_flower_1 <- as.raster(large_flower)

flower_small <- image_read("Images/PPCA_Plot/Flower_Small.png")
flower_small_1 <- as.raster(flower_small)
#############################################################################################################################################################
#COMPATIBILITY
#############################################################################################################################################################
#Load plots

#Invert axes
PC$S[,1] <- -PC$S[,1]
PC$S[,2] <- -PC$S[,2]

all_spp <- function(PC, x="PC1", y="PC2") {
  # PC being a prcomp object
  data <- data.frame(PC$S)
  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
  dat <- data.frame(x = data[,x], y = data[,y])

@@

  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density

  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.025, 0.050, 0.075), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.85),title="Kernel density"))+
    scale_alpha(guide = 'none')

    plot <- plot + geom_point(data=dat, aes(x, y),size=0.95, color="black")

  ########
  #ADD ARROWS 
  ########
  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
  mult <- min(
    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
  )
  datapc <- transform(datapc,
                      v1 = .7 * mult * (get(x)),
                      v2 = .7 * mult * (get(y))
  )
  # add arrows
  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1.6, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))

  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=1.2, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, colour=c("black"))

@@

@@

  plot <- plot + theme_bw() + annotation_raster(tree_1, xmin = -4, xmax = -2.9,ymin = 2.45, ymax = 4.35)+
     annotation_raster(style_l_1, xmin = 2.45, xmax = 3.25,ymin = 2.25, ymax = 3.35) +
    annotation_raster(style_s_1, xmin = -3.25, xmax = -2.45,ymin = -2.65, ymax = -1.75) +
    annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.15,ymin = -0.65, ymax = 0.25) +
    annotation_raster(ovule_l_1, xmin = -4.1, xmax = -3.5,ymin = -0.3, ymax = 0.6) +
    annotation_raster(selfing_n_1, xmin = -0.2, xmax = 1.2,ymin = 2.8, ymax = 4.7) +
    annotation_raster(selfing_h_1, xmin = -0.95, xmax = 0,ymin = -4.1, ymax = -3.25) +
    annotation_raster(single_flower_1, xmin = 3.0, xmax = 3.7,ymin = -2, ymax = -1.1) +
    annotation_raster(many_flowers_1, xmin = -4.60, xmax = -3.15,ymin = 1, ymax = 2.15) +
    annotation_raster(large_flower_1, xmin = 3.4, xmax = 4.2,ymin = 1, ymax = 2.1) +
    annotation_raster(flower_small_1, xmin = -4, xmax = -1.85,ymin = -2.4, ymax = -0.4) +
    annotation_raster(single_flower_1, xmin = 2.8, xmax = 3.5,ymin = -3, ymax = -2.2)

      #ADD LABELS
  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
 plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.5,5.5,7.5,7.3,6)), y = -(PCAloadings$PC2*c(4.77,2.4,3,6.5,14,5.5)),
                         label = PCAloadings$Variables, color="black",fontface =2,size=5)
